\documentclass[english]{lni}
% for German use:
%\documentclass{lni}

\IfFileExists{latin1.sty}{\usepackage{latin1}}{\usepackage{isolatin1}}

\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{listings} %if lstlistings is used
\usepackage{changepage} %for changing topmargin on first page
\usepackage[figurename=Fig., tablename=Tab., small]{caption}[2008/04/01]
\renewcommand{\lstlistingname}{List.}    % Listingname is now List. 

\usepackage[disable]{todonotes}

% multicollumn
\usepackage{multicol}
% *** SUBFIGURE PACKAGES ***
\usepackage[caption=false, font=normalsize, labelfont=sf, textfont=sf]{subfig}


%Beginning of page count for this paper
\setcounter{page}{1}

%head line settings
\pagestyle{fancy}
\fancyhead{} % clears the settings
\fancyhead[RO]{\small A. Br\"omme, C. Busch, C. Rathgeb and A. Uhl (Eds.): BIOSIG 2016, \linebreak Lecture Notes in Informatics (LNI), Gesellschaft f\"ur Informatik, Bonn 2016 \hspace{5pt} \thepage \hspace{0.05cm}}
\fancyfoot{} % clears footer settings
\renewcommand{\headrulewidth}{0.4pt} %horizontal line below header
\setcounter{footnote}{0}

\author{Jannis Priesnitz\footnote{University of Applied Sciences Darmstadt, Department of Computer Science, Schöfferstraße 3, 64295 Darmstadt \email{jannis.priesnitz@stud.h-da.de}}, Julian Thomae\footnote{University of Applied Sciences Darmstadt, Department of Computer Science, Schöfferstraße 3, 64295 Darmstadt \email{jueliant@gmail.com}}}


\title[Capabilities of face morphing]{Capabilities of automatic and manual face morphing}



\begin{document}
	
	\maketitle
	
	\renewcommand{\refname}{References}
	\setcounter{footnote}{2} %Change to the number of authors for a correct numbering of the foot notes
	
	\pagestyle{fancy}
	\fancyhead{} 
	\fancyhead[RO]{\small $<$firstname lastname [et. al.]$>$(Edt.): $
		<$book title$>$, \linebreak Lecture Notes in Informatics (LNI), 
		Gesellschaft f\"ur Informatik, Bonn $<$Jahr$>$ \hspace{5pt} 
		\thepage \hspace{0.05cm}}
	\fancyfoot{} 
	\renewcommand{\headrulewidth}{0.4pt} 
	\begin{abstract}
		In a common scenario one passport including its biometric features belongs to one person. This and only this person \textit{should be} successfully matched to the biometric picture which is in the persons passport in the situation of an Automatic Border Control (ABC). But what if two or more persons are successfully matched to one passport? With the procedure of morphing faces, it is possible to get a promising acceptance rate for both persons. This work compares an automatic with a manual approach for creating morphed faces. In addition the region, in which an sufficient match rate for both persons is reached, is determined to hide the second face as good as possible from manual inspection. 
		
	\end{abstract}
	\begin{keywords}
		Face morphing \and face detection \and automatic border controls
	\end{keywords}
	
%	\linebreak
	\pagestyle{fancy}
	\fancyhead{} 
	\fancyhead[RO]{\small Capabilities of face morphing \hspace{5pt} 
		\thepage \hspace{0.05cm}}
	\fancyhead[LE]{\hspace{0.05cm}\small \thepage \hspace{5pt} 
		Jannis Priesnitz and Julian Thomae}
	\fancyfoot{} 
	\renewcommand{\headrulewidth}{0.4pt}
	
		\input{Introduction}
		%\input{Fundamentals} no longer needed
		\input{Conception}
		\input{Detection_Algorithm}
		\input{Results}
		\input{Conclusion}
		\input{Further_topics}
		
	\bibliographystyle{lnig}
	\bibliography{Quellen}
	
\end{document}



